\documentclass[11pt]{article}
\usepackage[margin=0.8in]{geometry}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage{hyperref}
\usepackage{xcolor}

\hypersetup{
    colorlinks=true,
    urlcolor=blue,
}

\titleformat{\section}{\large\bfseries}{}{0em}{}[\titlerule]
\setlist[itemize]{noitemsep, topsep=0pt}

\begin{document}

\begin{center}
    {\LARGE \textbf{Swara Ramesh}} \\
    Incoming SWE Intern @ Axon, Summer 2026 \\
    \href{mailto:swara.ramesh@outlook.com}{swara.ramesh@outlook.com} \;|\;
    +1 (425) 891-8555 \;|\;
    \href{https://www.linkedin.com/}{LinkedIn} \;|\;
    \href{https://github.com/}{GitHub}
\end{center}

\vspace{0.2in}

\section*{Education}

\textbf{University of Washington} \hfill Seattle, WA \\
Dean’s List Scholar \\
Bachelor of Science: Computer Science \;|\; Minor: Applied Mathematics \hfill 2024 -- 2028

\vspace{0.05in}
\textbf{Relevant Coursework:} Data Structures and Algorithms, Artificial Intelligence, Software Design, Systems Programming, Discrete Math, Linear Algebra

\textbf{Activities:} Women In Computing Leadership, WebImpact, Husky Coding Project

\vspace{0.15in}

\section*{Experience}

\textbf{University of Washington} \hfill Seattle, WA \\

\textbf{Research Assistant | UbiComp Lab} \hfill October 2025 -- Present
\begin{itemize}
    \item Built an ML pipeline for the ExerciseRx clinical app, integrating pose-estimation inputs, feature engineering, and model training.
    \item Trained a scikit-learn Random Forest classifier on Mediapipe PoseLandmarker features, achieving 95\% accuracy in exercise phase classification.
    \item Processed 1,000+ frames per video to extract pose-landmark data and engineered movement-tracking, visibility-validation, and repetition-detection metrics.
\end{itemize}

\textbf{Research Assistant | SMARTS Lab} \hfill April 2025 -- Present
\begin{itemize}
    \item Engineered Android and iOS apps for ergonomic risk analysis, evaluating musculoskeletal disorder risk using REBA; deployed beta app with the Washington Retail Association.
    \item Built a real-time pose estimation pipeline integrating MediaPipe + CameraX + AVFoundation to extract and render 3D skeletal landmarks.
    \item Implemented recording, playback, and interactive time-series feature to analyze top medium/high-risk positions over time.
\end{itemize}

\textbf{Expedia} \hfill Seattle, WA \\
\textbf{Career Development Program - Software Engineering} \hfill July 2025 -- November 2025
\begin{itemize}
    \item Won the AI business challenge focused on enhancing Expedia’s hotel bookings feature.
    \item Designed and presented a chatbot booking feature to streamline and speed up the reservation process to Expedia engineers and program leaders.
\end{itemize}

\vspace{0.15in}

\section*{Projects}

\textbf{DubHacks | 2nd Place Winner (AWS Track)} \hfill Seattle, WA \\
\textbf{Wellify.ai | AI Healthcare Assistant} \hfill October 2025
\begin{itemize}
    \item Built a symptom-to-health-center matching system using an XGBoost model deployed on AWS SageMaker with speech-to-text input and AWS Bedrock for classification, optimizing patient routing based on real-time wait times, specialist availability, and symptom patterns across three University of Washington health centers.
    \item Integrated 6+ third-party APIs to MyChart prescriptions using a React frontend and FastAPI backend; utilized AWS Cognito for authentication with DynamoDB for secure user management.
    \item Integrated insurance chatbot leveraging AWS Bedrock (Claude 3.5 Sonnet LLM) \& RAG across 1,000+ insurance policy documents, visualizing facility-specific copays, deductibles, and service availability.
\end{itemize}

\textbf{EvacuAid | Natural Disaster Relief \& Evacuation Aid} \hfill October 2025
\begin{itemize}
    \item Utilized AWS Bedrock to develop an AI-focused backend to provide specialized evacuation routes and plans for the disabled and elderly in natural disasters.
    \item Integrated backend into a website designed in Figma for rapid disaster response planning.
\end{itemize}

\vspace{0.15in}

\section*{Skills}

\textbf{Programming Languages:} Java, Python, C, Kotlin, Swift, JavaScript, React, Xamarin, HTML/CSS \\
\textbf{Cloud \& Tools:} AWS, Git, Linux

\end{document}